Summary Dendro

### 2018-10-16 analysis/dendro_summary.Rmd
add na.rm TRUE

# average age 
age_sites <- rwl_stat_sites %>% 
  group_by(site) %>% 
  dplyr::summarise(age_mean = mean(year), 
         age_std = sd(year)) %>% as.data.frame()

@@

rwl_sites_summ <- rwl_stat_sites %>% 
  group_by(site) %>% 
  dplyr::summarise(n_trees = length(unique(tree)),
                   n_radii =n(), 
                   year_first = min(first), 
                   year_last = max(last), 
                   year_length = max(year),
                   rw_mean = mean(mean), 
                   rw_std = mean(stdev),
                   sens1 = mean(sens1), 
                   sens2 = mean(sens2), 
                   ar1 = mean(ar1)) %>% 
  as.data.frame()

>>>>

# average age 
age_sites <- rwl_stat_sites %>% 
  group_by(site) %>% 
  dplyr::summarise(age_mean = mean(year, na.rm = TRUE), 
         age_std = sd(year)) %>% as.data.frame()

@@

rwl_sites_summ <- rwl_stat_sites %>% 
  group_by(site) %>% 
  dplyr::summarise(n_trees = length(unique(tree)),
                   n_radii =n(), 
                   year_first = min(first), 
                   year_last = max(last), 
                   year_length = max(year),
                   rw_mean = mean(mean, na.rm = TRUE), 
                   rw_std = mean(stdev, na.rm = TRUE),
                   sens1 = mean(sens1, na.rm = TRUE), 
                   sens2 = mean(sens2, na.rm = TRUE), 
                   ar1 = mean(ar1, na.rm = TRUE)) %>% 
  as.data.frame()
